RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-03-02 paper/paper7/paper7.tex
4

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
Bosch et al. recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
\cite{BoschZapilkoWackerowEckert2015}\tb{ToDo: publish technical report}.

We distinguish two validation types:
\emph{Content-Driven Validation} contains the set of constraints ensuring that the data is consistent with the intended semantics of data models,
i.e. the integrity of the data according to data models.
\emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
We determined the default \emph{severity level} (\emph{R-158}) for each constraint indicating how serious the violation of the constraint is.
The continuum of severity levels ranges from informational via warning and error to fatal error. 
Although we provide default severity levels for each constraint, users should be able to specify the severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.

@@

@@

\subsection{Aggregated (Meta)Data}

@@

\subsection{Person-Level (Meta)Data}

@@

\subsection{Technology-Driven Validation}

>>>>

Bosch et al. identified in total \textcolor{red}{74} requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
\cite{BoschZapilkoWackerowEckert2015}.

We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models (sections \ref{aggregated-metadata-and-data}-\ref{person-level-metadata-and-data}).
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
The continuum of severity levels ranges from informational via warning and error to fatal error. 
Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.

@@

further ideas:

@@

\subsection{Aggregated Metadata and Data}
\label{aggregated-metadata-and-data}

@@

\subsection{Person-Level Metadata and Data}
\label{person-level-metadata-and-data}

@@

\subsection{Technology-Driven Validation}
\label{technology-driven-validation}
